Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-01-20 appendix.tex
moved appendix and larger legend

\documentclass{article}
\pdfpagewidth=8.5in
\pdfpageheight=11in
% The file ijcai21.sty is NOT the same than previous years'
\usepackage{ijcai21}
\usepackage{times}
\usepackage{soul}
\usepackage[hidelinks,hypertexnames=false]{hyperref}
\usepackage{amsthm}

%%% Load required packages here (note that many are included already).
\input{preamble/packages}
\input{preamble/math}
%for appendix
\usepackage{import}
\usepackage{algorithm, algpseudocode}
\usepackage{booktabs}
\usepackage{pgfplots}
\pgfplotsset{compat=1.16}

\setlist[itemize]{noitemsep, topsep=0pt}

\newcommand{\commentOC}[1]{\textcolor{blue}{\small$\big[$OC: #1$\big]$}}
\newcommand{\commentBN}[1]{\textcolor{red}{\small$\big[$BN: #1$\big]$}}
\newcommand{\commentPV}[1]{\textcolor{brown}{\small$\big[$PV: #1$\big]$}}

\pdfinfo{
	/TemplateVersion (IJCAI.2021.0)
}

%I find these settings useful in draft mode. Should be removed for final versions.
	%Which line breaks are chosen: accept worse lines, therefore reducing risk of overfull lines. Default = 200.
		\tolerance=2000
	%Accept overfull hbox up to...
		\hfuzz=2cm
	%Reduces verbosity about the bad line breaks. TODO reduce
		\hbadness 10000
	%Reduces verbosity about the underful vboxes.
		\vbadness=6000

%%% Use this command to specify the title of your paper.

\title{Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination}

%%% Provide names, affiliations, and email addresses for all authors.

\author{ID: 3177}

%\author{
%	Beatrice Napolitano$^1$\footnote{Contact Author}\and
%	Olivier Cailloux$^1$\and
%	Paolo Viappiani$^2$\\
%	\affiliations
%	$^1$Université Paris-Dauphine, Université PSL, CNRS, LAMSADE\\
%	$^2$LIP6, UMR 7606, CNRS and Sorbonne Universit\'e\\
%	\emails
%	\{beatrice.napolitano, olivier.cailloux\}@dauphine.fr,
%	paolo.viappiani@lip6.fr
%}

\newcommand{\BibTeX}{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em\TeX}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

\begin{abstract}
Social choice deals with the problem of determining a consensus choice from the preferences of different agents.
In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided.
This assumption of full preference information has recently been questioned by a number of researchers and
	several methods for eliciting the preferences of the agents have been proposed.
	%  are completely known have been proposed, as well as techniques that consider the opposite scenario.

In this paper we argue that in many situations one should consider as well the voting rule to be 	partially specified.
%	This article goes one step further by tackling one important new case, namely, when both the voting rule and the agents preferences are partially known. It also permits to obtain a progressively refined recommendation without requiring to achieve full knowledge of either sort of information.
%This is useful because providing such information is often costly: the chair may find it hard to specify a rule completely; agents may need time to form reflective preferences.	
	Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a concrete profile. In addition, we assume that the agent preferences also have to be elicited. %and are acquired by asking comparison queries. 
	We propose a method for robust approximate winner determination and interactive elicitation based on minimax regret; we develop several strategies for choosing the questions to ask to  the chair and the agents in order to %acquire the most relevant information for
converge quickly to a near-optimal alternative. Finally, we analyze these strategies in experiments %in order to validate our approach
 %focusing on settings 
 where the  rule and the preferences are simultaneously elicited.
 %and obtain practical guidelines.
\end{abstract}

\section{Introduction}
Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
In many situations, such as in group recommender systems, the goal is to find a consensus choice;
social choice theory can provide foundations for such applications.

%The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents (voters) are expressed beforehand. These represent two strong hypothesis.
The traditional approach to social choice assumes that 1) the full preference orderings of the agents and 2) the social choice function are expressed beforehand. These represent two strong hypothesis.

Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost).
This observation has motivated several works assuming partial preference orders: 
%and incremental elicitation of agent preferences. 
%In the context of social choice, several authors have been interested in obtaining information about winners with reduced assumptions about the knowledge of the agent preferences (assuming that the voting rule is known).
one early work is  by \Citet{Conitzer2005} who studied the complexity of communication when using different voting rules; %determining lower and upper bounds;
%they showed that, 
%in the worst case, the agents should send their complete set of preference for several rules. 
\Citet{Konczak05} studied the computation of possible and necessary winners for various voting rules; %and showed that the problem is hard in the general case.
\citet{Xia2008} then showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard;
% they also  proposed polynomial-time algorithms when using maximin and Bucklin.
additional complexity results were given by \citet{Walsh2007} and \citet{Pini2007}.
%\citep{Walsh2007} showed that the general case remains computationally hard even when restricting to single-peaked preferences;  sufficient conditions that ensure tractability were then found \citep{Pini2007}.

Since in many practical situations there would be too many possible winners but no necessary winners, several works addressed the problem of agent preferences elicitation using a variety of approaches (minimax regret, Bayesian methods, etc.) with the goal of converging to a necessary winner \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016,Dey2016_2}. Among those, \citet{Walsh2009} and \citet{Conitzer2009} analyzed when to stop the elicitation process.

A second concern is the ability of the chair (the person or organization supervising the voting process) to provide a precise definition of the voting rule, suggesting the relaxation of the second hypothesis. Indeed, it is often difficult for non-experts to formalize a voting rule on the basis of some generic preferences over a desired aggregation method. 
%Thus, the first hypothesis should also be relaxed. 
%While most of the focus in the research community has been in dealing with incomplete agent preferences, 
Consider, as an example, a chair that is about to hire a new employee, whose performances are evaluated by several experts. The members of the chair may not have a voting rule in mind at the start of the process, and might not wish to agree on a specific voting rule. However, they might be willing to answer a few questions requiring to select who should be the winner out of specific profiles. 
%The information provided can be used to   % to determine their employee of choice.

%This paper considers both sources of uncertainty at the same time, and proposes a method able to recommend a consensus choice without requiring full knowledge of either.
In this paper, we focus on positional scoring rules with convex weights, that are a particularly common method used to aggregate rankings. 
We develop methods, based on the notion of minimax regret, for determining a robust ``winner'' under uncertainty of both the voting rule and the agent preferences.
%alternative using positional scoring rules and 
We provide incremental elicitation methods that 
at each step of the elicitation question either one of the agents or the chair, and we discuss several heuristics to choose questions that quickly reduce the regret. 
Answers to questions are encoded as constraints; questions to the agents are comparisons between pairs of alternatives while
questions to the chair ask to select a winner out of a synthetic profile.

While some previous works have considered partially specified aggregation methods \citep{Stein1994,Llamazares2013,Viappiani2018}, we do not know of any work considering both sources of uncertainty at the same time. 
%has dealt with %scenarios where it is instead the voting rule that is partially defined. % but the preferences are given. 
%a  partially defined voting rule.
%While previous works have considered either partial information about the agent preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.
Actually, very few works altogether have considered the problem of eliciting a voting rule by asking questions to the chair. We mention the work of \Citet{Cailloux2014} that assumes a different representation for the rule. %we mention the work of \Citet{Cailloux2014} considering elicitation the voting rule by assuming a specific representation.
%A classic paper is the one by \citet{Stein1994} that, considering scoring rules, identified dominance relations between alternatives; these relations allow to determine pairs of alternatives where the first is at least as good as the second no matter which weights are chosen among a generic class of weights (decreasing weighs or convex decreasing weights).
%More recent articles considered the problem of dealing with unspecified weights in positional scoring rules: \citet{Llamazares2013} proposed a method based on Data Envelopment Analysis (DEA), while \citet{Viappiani2018} proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret). 
% provided an elicitation framework for a different class of rules.
Additionally, some works address the manipulability of voting rules \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011,Baumeister2019} and 
strategic behaviors \citep{Endriss2016,Lev2019,Annemieke2012}.

Our approach is evaluated on simulations with synthetic and real datasets where both the voting rule and the agent preferences are initially unknown to the system and incrementally revealed through questioning. We assume the chair to be human, thus able to answer questions about a limited number of alternatives, so we focus on small scale social choice situations. We compare the effectiveness of several questioning strategies based on the current knowledge of the rule and preferences. To summarize our contributions: 1) we provide a novel mechanism for eliciting a voting rule by translating abstract questions about weights to a choice of an alternative given a concrete profile; 2) we show that with our elicitation method it is possible to reach low regret with a reasonable number of questions; 3) we present elicitation strategies that achieve good results within reasonable computation time; 4) we show that for the class of rule considered, asking a few questions to the chair suffice to reach low regret; 5) our experiments suggest that low degree of similarity among preferences (as in impartial culture) is a more challenging setting than less varied profiles.
%\begin{itemize}
%	\item we provide a novel mechanism for eliciting a voting rule by translating abstract questions about weights to a choice of an alternative given a concrete profile;  
%	\item we showed that with our elicitation method %in small problem sizes, %starting with zero knowledge,
%	it is possible to reach low regret with a reasonable number of questions;
%	\item the elicitation strategies that we provide, in particular Pessimistic, achieve good results within reasonable computation time; %for small problem sizes;
%	\item we showed that for the class of rule considered, asking a few questions to the chair suffice to reach low regret;
%	\item our experiments suggest that low degree of similarity among preferences %rankings 
%	(as in impartial culture) is a more challenging setting than less varied profiles.
%\end{itemize}

\section{Social choice with partial information}
\label{sec:background}
We now introduce some basic concepts.
We consider a set $A$ of $m$ alternatives (products, restaurants, public projects, job candidates, etc.), an infinite set $\N$ of potential agents and a specific finite set of agents $N^* \subset \N$.

A {\em profile} $(\pref_j, j \in N)$ considers a finite subset of agents $N \subset \N$ and associates to each agent a preference order ${\pref_j}  \in \linors$, a linear order over the alternatives.
A profile is equivalently represented by $\profile=(v_j, j \in N)$ where $v_j(x) \in \set{1, \ldots, m}$ denotes the rank of alternative $x$ in the preference order $\pref_j$. 
A social choice function $f : \cup_{\emptyset ≠ N \subset \N} \linors^N \rightarrow \powersetz{A}$ associates to each profile a set of (tied) winners, where $\powersetz{A}$ is the powerset of $A$ excluding the empty set.
Among the many possible social choice functions, we consider convex {\em positional scoring rules (PSRs)}. A PSR $f^{\w}$ is parameterized by a \emph{scoring vector} $\w$ associating weights $w_r \in [0, 1]$ to positions, with $1 = w_1 ≥ w_2 ≥ … ≥ w_m = 0$.
Let $\alpha^{x}_r$ be the number of times that alternative $x$ was ranked in the $r$-th position.
Given $\profile$ and $\w$, an alternative $x \in A$ obtains the score
\begin{align}
	\label{eq:srule}
	s(x; \profile, \w) = \sum_{j=1}^{n} w_{v_j(x)}
	= \sum_{r=1}^{m} \alpha^{x}_r w_r\ .
\end{align}
The winners $f^{\w}(\profile)$ are the alternatives with highest score.

An important class of PSRs is the one using convex weights \citep{Stein1994,Llamazares2016}, meaning that the difference between the weight of the first position and the weight of the second position is at least as large as the difference between the weights of the second and third positions, etc.
\begin{equation} 
	\label{eq:convexity}
	\forall r \in \{1,\ldots,m-2\}: w_r - w_{r+1} \geq w_{r+1}-w_{r+2}.
\end{equation}
The constraint above is a natural and common assumption, often used when aggregating rankings in sport competitions (such as F1 racing, alpine skiing world cup); losing ranks at the top  is more damaging than losing ranks at the bottom.
Let $\W$ denote the set of such convex weight vectors.

Let $\profile^* = (\pref_j^*, j \in N^*)$ and $\w^*$ denote the profile and weight vector, unknown to us, that represent the preferences of the agents in $N^*$ and of the chair.

At a given time, our knowledge of agent $j$'s preference is encoded by a partial order ${\ppref_j} \subseteq {\pref_j^*}$ over the alternatives, a transitive and asymmetric relation (we assume that preference information is truthful).
%We use $\prefinc$ to denote incomparability, that is $a \prefinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
An incomplete profile $\pprofile = (\ppref_j, j \in N^*)$ maps each agent to a partial preference.
Let $C(\ppref_j) = \set{{\succ} \in \linors \suchthat {\ppref_j} \subseteq {\succ}}$ denote the set of possible completions of $\ppref_i$ and $C(\pprofile) = \prod_{j \in N} C(\ppref_j)$ the set of complete profiles extending $\pprofile$. Note that $\profile^* \in C(\pprofile)$.

The vector $\w^*$  is also unknown but we assume that the chair is able to specify additional preference information taking the form of linear constraints about $\w^*$. Let $\pw \subseteq \W$ denote the set of weight vectors compatible with the preferences expressed by the chair about the scoring vector.
%Of course it may be difficult for real decision makers to state preferences about the voting rule in such an abstract way.
We will show in \cref{sec:elicit} that the additional preferences we use can be elicited by showing a complete profile of a synthetic election and asking who should be elected in this case.

\section{Robust winner determination}
\label{sec:mmr}
It is desirable in an elicitation protocol such as ours to be able to stop before reaching full knowledge of the agent preferences or of the preferences of the chair about the voting rule. As, often, there are no necessary winners and too many possible winners, it is useful to declare a winner given partial information.
As a decision criterion to determine a winner, we propose to use minimax regret \citep{Savage1954}. 
This decision criterion has been used for robust optimization under data uncertainty \citep{Kouvelis1997} as well as in decision-making with uncertain utility values \citep{Salo2001,Boutilier2006}.
In particular, \citet{Lu2011} have adopted minimax regret for winner determination in social choice where
the preferences of agents are partially known, while the social choice function is known.

We consider the simultaneous presence of incomplete knowledge in agent preferences and in the weights of the PSR.
We use \emph{maximum regret} to quantify the worst-case error, and let the alternatives that minimize this quantity win, giving some robustness in face of ignorance.
Intuitively, the quality of a proposed alternative $a$ is how far $a$ is from the optimal one in the worst case, given the current knowledge.

Given $\pprofile$ and $\pw$ (that represent the current knowledge about agent preferences and the PSR),
the maximum regret is considered by assuming that an adversary can both 1) extend the partial profile $\pprofile$ into a complete profile, and 2) instantiate the weights choosing among any weight vector in $\pw$. %where $\pprofile$ and $\pw$ represent our knowledge so far.
We formalize the notion of minimax regret in multiple steps.
First of all, $\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w)$ is the “regret” of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$.
The pairwise maximum regret $\PMR(x,y;\pprofile,W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w)$ of $x$ relative to $y$ given the partial profile $\pprofile$ and the set of weights $W$
is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights.
The maximum regret $\MaxR(x;\pprofile,W) = \max_{y \in A} \PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x; \profile, \w)$ is the worst-case loss of $x$. That is the loss occurred as the result of an adversarial selection of the complete profile $\profile \in C(\pprofile)$ and of the scoring vector $\w \in W$ that together maximize the loss between $x$ and the true winner under $\profile$ and $\w$.
Finally,  $\MMR(\pprofile,W) = \min_{x \in A} \MaxR(x;\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W} \in A^*_{\pprofile, W} = \argmin_{x \in A} \MaxR(x;\pprofile,W)$.
Picking as consensus choice an alternative associated with minimax regret provides a recommendation that gives worst-case guarantees. 
In cases of ties in minimax regret, we can return all minimax alternatives $A^*_{\pprofile, W}$ as winners or pick one of them using some tie-breaking strategy.

Observe that if $\MMR(\pprofile, W)\!=\!0$, then any $x^{*}_{\pprofile,W} \in A^*_{\pprofile, W}$ is a necessary winner: any valid completion of the profile and choice of $w \in W$ gives to $x^{*}_{\pprofile,W}$ the highest score.

We note that our notion of regret gives some cardinal meaning to the scores: instead of just being used to select winners under the corresponding PSR, their differences are considered as representing the regret of the chair.

% Add some general remarks about using minimax regret

\paragraph{Computation of minimax regret}
Given a voting rule and a partially specified profile, \citet{Xia2008} determine necessary winners by showing constructions that attempt to maximize the score difference between a proposed winner and a chosen alternative. This reasoning was later adopted by \citet{Lu2011} who used the considerations on the worst-case completions for computing the minimax regret.

In order to compute pairwise maximum regret, and therefore minimax regret, we decompose the PMR into the contributions associated to each agent by adapting this same reasoning to our setting. The context is however more challenging due to the presence of uncertainty in the weights.

Recall that, in the computation of $s(x; \profile, \w)$, $w_{v_j(x)}$ represents the score that $x$ obtains in the ranking $v_j$ (see \cref{eq:srule}).
Since scoring rules are additively decomposable, we can consider separately the contribution of each agent to the total score. Thus, we can write the actual regret of choosing $x$ instead of $y$ as $s(y; \profile,\w) - s(x; \profile, \w) = \sum_{j=1}^n w_{v_j(y)} - w_{v_j(x)}$, and we obtain $\PMR(x,y; \pprofile, W) =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]$.
%Note that in general the inner max depends on the weights chosen by the outer max.

The following propositions (with proofs in appendix) show that the procedure for completing a partial profile,  proposed by \citet{Lu2011} when considering a fixed weight vector, also applies in our setting. We write $a \pprefeq_j b$ iff $a \ppref_j b \lor a = b$ and adopt the canonical notation when considering a relation as a function, writing ${\pprefeq_j}(x)$ for $\set{y \suchthat x \pprefeq_j y}$.

\begin{proposition} \label{claim:completion}
	There exists a completion $\hat{\profile} \in C(\pprofile)$ of the profile $\profile$ such that $\PMR(x,y; \pprofile, W) = \max_{\w \in W} [ s(y; \hat{\profile}, \w) - s(x; \hat{\profile}, \w) ]$ and such that the linear order $\hat{v}_{j}$ of each agent $j$ satisfies:
	\begin{align} 
		\label{eq:complx}
		a \pref_j x &⇔ ¬(x \pprefeq_j a)\\
		\label{eq:comply}
		y \pref_j a &⇔ ¬(a \pprefeq_j y) ∧ ¬((x \pprefeq_j y) ∧ ¬(x \pprefeq_j a)).
	\end{align} 
\end{proposition}

\begin{proposition} \label{claim:rankPMR}
	The rank of $x$ in the PMR-maximizing linear orders of agent $j$ is $\hat{v}_{j}(x) = 1+\card{A}-\card{{\pprefeq_j}(x)}$, and the rank of $y$ is $\hat{v}_{j}(y)=1+\card{{\pprefinv_j}(y)}+\card{\beta}$, where $\card{\beta} = \card{A \setminus ({\pprefeq_j}(x) \cup {\pprefinv_j}(y))}$ if $(x \pprefeq_j y)$ and $\card{\beta} = 0$ otherwise.
\end{proposition}
Note that in \cref{claim:rankPMR}, in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.
\begin{proposition}\label{claim:PMR}
	The $\PMR$ can be written as:
	\begin{align} 
		\PMR(x,y; \pprofile, W)  
		& = \max_{w \in W} \sum_{j=1}^n w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} \\ 
		& = \max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i. 
	\end{align}
	where $\hat{\alpha}_{r}^{y}$ (resp. $\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp. $x$) has rank $r$ in the complete profile $\hat{\profile}$ defined in \cref{claim:rankPMR}. 
\end{proposition}
%\cref{claim:rankPMR} can be understood by observing that in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.
\cref{claim:PMR}  shows that PMR is linear in the weights.
%Recall that $\pw$ represents the weight vectors compatible with the preferences of the chair stated so far.
The pairwise max regret $\PMR(x,y; \pprofile,W)$ can thus be obtained by solving the following linear program defined on the variables $w_1, …, w_m$:
\begin{align}
	\max_{\w} & \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_{r}\\
	\text{ s.t. } & w_1 = 1 ≥ … ≥ w_m = 0, \text{\cref{eq:convexity}} \text{ and } \w \in \pw.
\end{align}
%Note that given our choice $w_{1}=1$ and $w_{m}=0$, there are only $m-2$ variables 
%(we leave $w_{1}$ and $w_{m}$ in the LP just for clarity of presentation).
The max regret $\MaxR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with all other alternatives in $A$, and the recommended alternatives are the ones with least max regret. 
Observe that when the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we do not need to further evaluate $x$. 
This idea can be exploited using a minimax-search tree \citep{Braziunas2012}.

\section{Interactive Elicitation} 
\label{sec:elicit}
We propose an incremental elicitation method based on minimax regret.
At each step, the system may ask a question either to one of the agents about her preferences or to the chair about the voting rule. 
The goal is to obtain relevant information to reduce minimax regret as quickly as possible.
The elicitation can be terminated either after a given number of questions, or when the minimax regret is lower than a threshold (or when it drops to zero if we wish optimality).

%As termination condition of elicitation, we can check whether minimax regret is lower than a threshold; or after having asked a given number of questions.
%if we wish optimality, we can perform elicitation until minimax regret drops to zero.

%The remainder of this section is structured as follows.
%First, we discuss the different types of questions that can be asked to the agents and to the chair, and the way responses are handled.
%Then, we describe different strategies to determine informative queries to ask next, with the goal of reducing $\MMR(\pprofile,W)$ quickly.

\paragraph{Question types}
We distinguish between questions asked to the agents and questions asked to the chair.
As {\em questions asked to the agents} we consider comparison queries relating two alternatives.
%Another common type of queries are {\em top-k}, asking to each agent her $k$ most preferred alternatives.
The effect of a response to a question asked to an agent is the increase in our knowledge about the agent rankings, thus augmenting the partial profile $\pprofile$. 
If agent $j$ answers a comparison query stating that alternative $a$ is preferred to $b$, then the partial order $\ppref_j$ is augmented with $a \ppref_j b$ and by transitive closure.

A bit more discussion is needed about {\em questions asked to the chair}.
Such questions aim at refining our knowledge about the scoring rule; a response gives us a constraint on the weight vector $\w$.
In particular, we want to obtain constraints of the type $w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2})$ for $r \in \{1,\ldots,m-2\}$, relating the difference between the importance of ranks $r$ and $r+1$ with the difference between ranks $r+1$ and $r+2$.

\paragraph{Building concrete questions for the chair}
Even if the chair might be considered able to answer directly such abstract questions, we want to ensure that these questions can also, in principle, be asked in a more concrete way: in terms of winners of example profiles. Such questions have clear semantics whose understanding can be assumed to be shared by the chair, contrary to abstract questions about weights. 
Moreover, this way of questioning the chair is independent of the voting rule that is being elicited. Questions about weights only make sense when considering PSRs.
Asking who should win in specific profiles has been used in experimental settings investigating the feeling of justice of individuals \citep{Giritligil2005}, but, to the best of our knowledge, the use of such questions to systematically guide an elicitation process about voting rules is novel. 
This is similar to favor, in decision theory, direct choice questions ("please choose either a or b") compared to, say, questioning the decision maker about the shape of her utility function. The former are considered “observable”: acts of choice are translated to preference statements \citep[Ch.\ 1]{colell_microeconomic_1995}.

Thus, our task is to build a profile, given $\lambda$ and $r ≤ m-2$, in such a way that the set of (tied) winners picked by the chair reveals whether $w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2})$.
\begin{proposition}\label{prop:chairQuestions}
	Given a rational $\lambda = p/q > 1$ and a rank $r$ between $1$ and $m - 2$, there exists a profile $P$ such that, for any weight vector $\w \in \W$, $a \in f(P)$ iff $w_{r} - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$ and $b \in f(P)$ iff $w_{r} - w_{r+1} ≤ \lambda (w_{r+1} - w_{r+2})$, where $f$ is the PSR parameterized with $\w$.
\end{proposition}

\begin{example*}
	Suppose we want to ask the following question to the chair: $w_{2} - w_{3} ≥ 2 (w_{3} - w_{4})$. 
	We then show the following profile to the chair and ask who should win (each column is a preference of an agent).
	\begin{center}
		$
		\begin{array}{ccccccccc}
			c&d&d&a&a&a&b&b&b\\
			a&c&c&b&b&b&a&a&a\\
			b&b&b&c&c&c&d&d&d\\
			d&a&a&d&d&d&c&c&c\\
		\end{array}.
		$
	\end{center}
	Both $a$ and $b$ have scores higher than $c$ and $d$ for all convex weights, thus either $a$ or $b$ will be picked under our hypothesis; and $s(a) ≥ s(b) ⇔ w_2 + 2 w_4 ≥ 3 w_3$.
	(\cref{proof:chairQuestions} presents the general method of constructing such profile.)
\end{example*}

\paragraph{Elicitation strategies}
We develop several strategies for simultaneous elicitation of agent preferences and of the PSR.
While it is of course possible to first fully elicit the agent preferences and afterwards elicit weights, we want to investigate approaches that are able to recommend winning alternatives before obtaining complete knowledge of the profile or the rule.
%Indeed, it can be beneficial to split efforts asking questions to the chair and to agents, depending on which is estimated to be more informative.
We define here the various strategies we tested experimentally. A strategy tells us, given the current partial knowledge $(\pprofile, W)$, which question to ask next.

The \strat{Random} strategy gives a baseline for comparison and informs about the difficulty of an elicitation problem. 
It first chooses equiprobably whether to question the chair or the agents. In the first case, it draws one rank in $1 ≤ r ≤ m-2$ equiprobably, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
%The intervals are initialized to $[1, n]$: $\lambda≥1$ by convexity and we assume $\lambda≤n$ wlog, in fact for $\lambda≥n$, the rule coincides with Plurality.
In the second case, it draws equiprobably among the agents whose preference is not known entirely; draws an alternative $a$ equiprobably among those involved in some incomparabilities in $\ppref_j$; and draws an alternative $b$ equiprobably among those incomparable with $a$ in $\ppref_j$.

Let $(x^{*},\bar{y}, \bar{\profile}, \bar{\w})$ be the current solution of the minimax regret, where $x^{*}$ is the minimax optimal alternative and $\bar{y}, \bar{\profile}, \bar{\w}$ the corresponding adversarial choices. 
The \strat{Pessimistic} strategy considers a set of $n + (m-2)$ candidate questions: one per agent, and one per rank (excluding the first and the last one which are known).

The candidate questions to the agents are chosen by extending the idea of \citet{Lu2011}, that priviledge learning about the relationship of $x^*$ and $\bar{y}$ to the other alternatives if possible.
	Given $j \in N^*$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, %the candidate question
	it concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random. 
%Responses to questions involving $x^*$ or $\bar{y}$ constrain the ability of the adversary to complete the profile in such manner, possibly reducing minimax regret.

The candidate questions to the chair are determined as in the Random strategy.

	Once having selected $n + m - 2$ candidate questions, the Pessimistic strategy selects the one that leads to minimal regret in the worst case.
	%, considering both possible answers to the question, and with penalty terms depending on the kind of question. To define this comparison precisely, 
	Assume that a question $q_1$ has type $t_1$ (being “chair” or “agent”), and leads to the new knowledge states $(\pprofile_1, W_1)$ if answered positively and $(\pprofile'_1, W'_1)$ if the answer is negative. 
	Define $R^{\max}_1 = \max\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)}$
	and $R^{\min}_1 = \min\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)} \epsilon_{t} + \epsilon'_{t}$.
	%If $(\pprofile_1, W_1) ≥ (\pprofile'_1, W'_1)$, define $\MMR^{\max} = \MMR(\pprofile_1, W_1)$ and $\MMR^{\min} = \MMR(\pprofile'_1, W'_1)$; otherwise, define $\MMR^{\max} = \MMR(\pprofile'_1, W'_1)$ and $\MMR^{\min} = \MMR(\pprofile_1, W_1)$.
	% and and $(\pprofile^\min_2, W^\min_2)$. numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$. Then the badness of the question in the worst case is:
	The terms $\epsilon_t$ and $\epsilon'_{t}$ are real numbers associated to the type $t$ of question; these parameters are used to fine tune the choice of the question type. 
	Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for  $q_2$.
	%We are now faced with the problem of aggregating these values in order to compare the informative values of the candidate questions.  \footnote{We adopt a pessimistic approach, reported to perform better than optimistic aggregation \citep{Cailloux2014}, although Our experiments in this context suggested a weak impact of that choice on the performance of the strategy.}
	%To avoid the absorption property of the max, we adopt $\leximax$ as an aggregator.
	Pessimistic considers question $q_1$ to be better  than $q_2$ iff $R^{\max}_1 < R^{\max}_2 \text{ or } [R^{\max}_1 = R^{\max}_2 \text{ and } R^{\min}_1 < R^{\min}_2]$.
	%This comparison gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
	%The motivation for using this operator lies in 
	In other words if the maximal {\em a posteriori} MMR of two questions are (nearly) equal, then it considers the (penalized) minimal MMR values, preferring the question with the lowest value.
	%(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal MMR values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal MMR.)

The \strat{Extended pessimistic} strategy uses the same criterion as the pessimistic strategy, but extending it to a bigger set of candidate questions, the same as those considered by the Random strategy. These candidate questions are then evaluated using the same operator as for the Pessimistic strategy.
%We use this strategy to test whether Pessimistic performs well: depending on the quality of the heuristic of the Pessimistic strategy, it might perform nearly equally well, or perhaps even better, than Extended pessimistic, while being (much) faster. 
Extended pessimistic is applicable only to very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute MMR twice, whose complexity is $O(nm^3)$.

>>>>

\documentclass{article}
\pdfpagewidth=8.5in
\pdfpageheight=11in
% The file ijcai21.sty is NOT the same than previous years'
\usepackage{ijcai21}
\usepackage{times}
\usepackage{soul}
\usepackage[hidelinks,hypertexnames=false]{hyperref}
\usepackage{amsthm}
\usepackage{xr}
\externaldocument{minimax}
%%% Load required packages here (note that many are included already).
\input{preamble/packages}
\input{preamble/math}
%for appendix
\usepackage{import}
\usepackage{algorithm, algpseudocode}
\usepackage{booktabs}
\usepackage{pgfplots}
\pgfplotsset{compat=1.16}
\begin{document}

\appendix
\section{Appendix}
\label{sec:appendix}
\newtheorem*{details*}{Strategy Details}
This appendix provides proofs for the propositions presented in the paper together with an additional table of experimental results.
\begin{sketch*}[\cref{claim:completion}]
	Consider our knowledge $\pprefeq_j$ about the preference of the agent $j$. 
	The adversary's goal is to make the score of $y$ as high as possible and the score of $x$ as low as possible. 
	To do this, he should complete $\ppref_j$ to $\pref_j$ by putting above $x$ as many alternatives as he can, that is, all the alternatives except those that are known to be worse than $x$ (those $a$ such that $x \pprefeq_j a$); and similarly, he should put below $y$ all the alternatives he can. Two conditions must be excluded for $a$ to go below $y$. The alternatives such that $a \pprefeq_j y$ can’t be put below $y$.
	Furthermore, the first objective must take priority over the second one: when an alternative should go above $x$ according to the first objective (because $¬(x \pprefeq_j a)$), and $x$ is known to be better than $y$ (thus $x \pprefeq_j y$), then $a$ should be put above $x$ (irrespective of whether $a \pprefeq_j y$), which will move both $x$ and $y$ one rank lower than if $a$ had been put below $y$. 
	This maximizes the adversary’s interests: because the weight vector is convex, the difference of scores will be lower when both alternatives are ranked lower (Equation \ref{eq:convexity}), and that difference of scores is in favor of $x$ when $x \ppref_j y$, thus to be minimized from the point of view of the adversary.
\end{sketch*}
